Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex
shrink

\help{6. explain the features of "datastructure-driven programming" that are used here in this problem. i.e. explicit temporary, bytemap format, transpositions}.
\begin{figure}
    \label{fig:spgemm_small}
	\includegraphics[width=\linewidth]{spgemm_small_speedup_log_scale.png}
    \caption{A comparison of several matrix multiplication algorithms between Finch and Taco smaller matrices, ordered from small to big dimension. Note that inner products necessarily requires $O(n^2)$ work and taco's outer products format is dense. Finch can use a sparse outer products format and thus has an asymptotic advantage that becomes evident as the output dimensions grow.}
\end{figure}

\begin{figure}
\label{fig:spgemm_large}
	\includegraphics[width=\linewidth]{spgemm_joel_speedup.png}
    \caption{A comparison of gustavson's algorithm between Finch and Taco on some larger matrices}
\end{figure}

>>>>

\help{6. explain the features of "datastructure-driven programming" that are used here in this problem. i.e. explicit temporary, bytemap format, transpositions}.
\begin{figure}
    \label{fig:spgemm}
	\includegraphics[width=0.5\linewidth]{spgemm_small_speedup_log_scale.png}%
	\includegraphics[width=0.5\linewidth]{spgemm_joel_speedup.png}
    \caption{A comparison of several matrix multiplication algorithms between
    Finch and Taco. On left, we use smaller matrices, ordered from small to big
    dimension. Note that inner products necessarily requires $O(n^2)$ work and
    taco's outer products format is dense. Finch can use a sparse outer products
    format and thus has an asymptotic advantage that becomes evident as the
    output dimensions grow. On right, we use only gustavson's algorithm and compare on larger matrices.}
\end{figure}
